Demographic Variables Plotted Against DVs(combined dataset)

### 2022-04-10 combined data set/demographicvariables.Rmd
added benefit graphs to demographic variables file. knitted both files to pdf

---
title: "demographic variables"
output:
  html_document:
    fig_width: 9
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
---

@@

```{r, eval=TRUE}

@@

```{r}

@@

cenrisksummary
```

##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender and caste groups

@@

castegendereffect$Gender_Caste <- as.factor(castegendereffect$Gender_Caste)
levels(castegendereffect$Gender_Caste)

@@

##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender and caste groups

@@

##Perceived Risk Scores for centrally managed hydroelectric dams by gender and caste groups

@@

castegendereffect %>%
  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin","Male_ST","Male_Brahmin", "Male_SC","Female_General","Male_General", "Female_OBC", "Female_ST","Female_SC", "Male_OBC")))%>%
  select(!starts_with(c("Risky_IND")))%>%
  select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
  na.omit()%>%
  dplyr::group_by(Gender_Caste)%>%
  summarise(hydro_m=mean(Risky_Hydro), hydro_sd=sd(Risky_Hydro), nuclear_m=mean(Risky_Nuclear), nuclear_sd=sd(Risky_Nuclear),            coal_m=mean(Risky_Coal),   coal_sd=sd(Risky_Coal))%>%
  arrange(desc(hydro_m))%>%
  ggplot(aes(y = Gender_Caste, x = hydro_m))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(xmin=hydro_m-hydro_sd, xmax=hydro_m + hydro_sd), width=.2,
                 position=position_dodge(.9))+
  labs(x = "mean perceived risk", y = "GenderXCaste groups")
```

##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent

```{r}

joineddf$urban_rural <- as.factor(joineddf$urban_rural)
class(joineddf$urban_rural)
levels(joineddf$urban_rural)

@@

##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender

```{r}

joineddf$gender <- as.factor(joineddf$gender)
class(joineddf$gender)
levels(joineddf$gender)

@@

##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender.

@@

joineddf$gender <- as.factor(joineddf$gender)
class(joineddf$gender)
levels(joineddf$gender)

@@

##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by religion

@@

joineddf$religion <- as.factor(joineddf$religion)
class(joineddf$religion)
levels(joineddf$religion)

joineddf %>%
  select(starts_with(c("Risky", "religion")))%>%
  select(!starts_with(c("Risky_IND", "religiontext")))%>%
 mutate(religion = factor(religion, levels = c("Agnostism/ Atheism","Other (Please mention)" ,  "Jainism", "Buddhism", "Islam",              "Hinduism", "Christanity", "Sikhism"))) %>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
  select(religion, riskscore) %>%
  dplyr::group_by(religion)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= religion, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  coord_flip()
```

##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by religion.

@@

joineddf$religion <- as.factor(joineddf$religion)
class(joineddf$religion)
levels(joineddf$religion)

joineddf %>%
  select(!starts_with(c("religiontext")))%>%
  select(starts_with(c("Risky_IND", "religion")))%>%
 mutate(religion = factor(religion, levels = c("Agnostism/ Atheism", "Jainism","Other (Please mention)" ,  "Buddhism", "Islam",              "Hinduism", "Christanity", "Sikhism"))) %>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
  select(religion, riskscore) %>%
  dplyr::group_by(religion)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= religion, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  coord_flip()
```

##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by age

@@

joineddf$age <- as.factor(joineddf$age)
class(joineddf$age)
levels(joineddf$age)

joineddf %>%
  select(starts_with(c("Risky", "age")))%>%
  select(!starts_with(c("Risky_IND")))%>%
 mutate(age = factor(age, levels = c("18-24 years old", "25-34 years old", "35-44 years old", "45-54 years old" , "55-64 years old" ,  "65-74 years old", "75 years or older"))) %>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
  select(age, riskscore) %>%
  dplyr::group_by(age)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= age, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  coord_flip()
```

##Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by age.

@@

joineddf$age <- as.factor(joineddf$age)
class(joineddf$age)
levels(joineddf$age)

joineddf %>%
  select(starts_with(c("Risky", "age")))%>%
  select(starts_with(c("Risky_IND", "age")))%>%
 mutate(age = factor(age, levels = c("18-24 years old", "25-34 years old", "35-44 years old", "45-54 years old" , "55-64 years old" ,  "65-74 years old", "75 years or older"))) %>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
  select(age, riskscore) %>%
  dplyr::group_by(age)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= age, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  coord_flip()
```

##Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by state

@@

joineddf$State <- as.factor(joineddf$State)
class(joineddf$State)
levels(joineddf$State)

cenrisksummary %>%
  mutate(technology = fct_reorder(technology, mean, .desc = TRUE))%>%
  ggplot(aes(y= technology, x= mean, fill = technology))+
  geom_bar(stat="identity", position=position_dodge())+
  theme_minimal()+
  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  scale_fill_manual(values=c("#74238B", "#FEF102","#484349","#BA5C12", "#4D9DE0","#CFEBDF", "#FA6728"))+
  xlim(0,5)+
  facet_wrap(~ State)
  #scale_fill_manual(y, values =))+

@@

#Distribution checks

```{r}
joineddf %>%
  filter(urban_rural == "Rural") %>%
  ggplot(aes(x=Risky_Hydro, y = ..count..), fill = "lightgray")+
  geom_density()
```

>>>>

---
title: "Demographic Variables Plotted Against DVs(combined dataset)"
output:
  pdf_document: 
    toc: yes
    number_sections: yes
    toc_depth: 2
    fig_width: 9
    fig_height: 6
    fig_caption: yes

  html_document:
    fig_width: 9
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged
---

@@

```{r, eval=TRUE, echo=FALSE}

@@

```{r, echo = FALSE}

@@

## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender and caste groups

@@

castegendereffect$Gender_Caste <- as.factor(castegendereffect$Gender_Caste)
#levels(castegendereffect$Gender_Caste)

@@

## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender and caste groups

castegenderben <- joineddf %>%
  select(starts_with(c("Ben", "gender", "caste")))%>%
  unite("Gender_Caste", c("gender", "caste")) %>%
  na.omit()

 # mean benefit from centrally controlled energy technologies

castegenderben %>%
  mutate(Gender_Caste = factor(castegenderben$Gender_Caste, levels = c("Male_OBC","Female_Brahmin","Male_SC","Male_ST", "Male_General", "Female_SC", "Female_OBC",  "Female_General" , "Male_Brahmin","Female_ST")))%>%
  select(!starts_with(c("Ben_IND")))%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
  select(Gender_Caste, benscore) %>%
  dplyr::group_by(Gender_Caste)%>%
  summarise(mean=mean(benscore), sd=sd(benscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(y = Gender_Caste, x = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(x = "mean perceived risk", y = "GenderXCaste groups")

## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender and caste groups

@@

## Perceived Benefit Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender and caste groups

# mean benefit from individually or community owned energy technologies

castegenderben %>%
  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Male_OBC","Female_SC","Female_Brahmin","Female_OBC","Male_SC", "Male_General","Male_ST","Female_General","Male_Brahmin", "Female_ST")))%>%
  select(starts_with(c("Ben_IND", "Gender_Caste")))%>%
  #select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(benscore = mean(c_across(Ben_INDHydro:Ben_INDLPG))) %>%
  select(Gender_Caste, benscore) %>%
  dplyr::group_by(Gender_Caste)%>%
  summarise(mean=mean(benscore), sd=sd(benscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(y = Gender_Caste, x = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(x = "mean perceived benefit", y = "GenderXCaste groups")

## Perceived Risk Scores for centrally managed hydroelectric dams by gender and caste groups

@@

castegendereffect %>%
  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Female_Brahmin","Male_ST","Male_Brahmin", "Male_SC","Female_General","Male_General", "Female_OBC", "Female_ST","Female_SC", "Male_OBC")))%>%
  select(!starts_with(c("Risky_IND")))%>%
  select("Risky_Hydro", "Risky_Nuclear", "Risky_Coal","Gender_Caste")%>%
  na.omit()%>%
  dplyr::group_by(Gender_Caste)%>%
  summarise(hydro_m=mean(Risky_Hydro), hydro_sd=sd(Risky_Hydro), nuclear_m=mean(Risky_Nuclear), nuclear_sd=sd(Risky_Nuclear),            coal_m=mean(Risky_Coal),   coal_sd=sd(Risky_Coal))%>%
  arrange(desc(hydro_m))%>%
  ggplot(aes(y = Gender_Caste, x = hydro_m))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(xmin=hydro_m-hydro_sd, xmax=hydro_m + hydro_sd), width=.2,
                 position=position_dodge(.9))+
  labs(x = "mean perceived risk", y = "GenderXCaste groups")
```
## Perceived Benefit Scores for centrally managed hydroelectric dams by gender and caste groups

castegenderben %>%
  mutate(Gender_Caste = factor(Gender_Caste, levels = c("Male_OBC","Male_ST", "Female_Brahmin","Male_SC","Male_General", "Female_SC","Female_General","Female_OBC","Male_Brahmin",  "Female_ST")))%>%
  select(!starts_with(c("Ben_IND")))%>%
  select("Ben_Hydro", "Ben_Nuclear", "Ben_Coal","Gender_Caste")%>%
  na.omit()%>%
  dplyr::group_by(Gender_Caste)%>%
  summarise(hydro_m=mean(Ben_Hydro), hydro_sd=sd(Ben_Hydro), nuclear_m=mean(Ben_Nuclear), nuclear_sd=sd(Ben_Nuclear),            coal_m=mean(Ben_Coal),   coal_sd=sd(Ben_Coal))%>%
  arrange(desc(hydro_m))%>%
  ggplot(aes(y = Gender_Caste, x = hydro_m))+
  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
  geom_errorbar(aes(xmin=hydro_m-hydro_sd, xmax=hydro_m + hydro_sd), width=.2,
                 position=position_dodge(.9))+
  labs(x = "mean perceived benefit", y = "GenderXCaste groups")
```

## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent

joineddf$urban_rural <- as.factor(joineddf$urban_rural)
#class(joineddf$urban_rural)
#levels(joineddf$urban_rural)

@@

## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by urban or rural location of the respondent

joineddf %>%
  select(starts_with(c("Ben", "urban_rural")))%>%
  select(!starts_with(c("Ben_IND")))%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
  select(urban_rural, benscore) %>%
  dplyr::group_by(urban_rural)%>%
  summarise(mean=mean(benscore), sd=sd(benscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= urban_rural, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(x = "urban or rural", y = "mean benefit")
```

## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender

```{r, echo =FALSE}

joineddf$gender <- as.factor(joineddf$gender)
#class(joineddf$gender)
#levels(joineddf$gender)

@@

## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by gender

```{r, echo =FALSE}

joineddf %>%
  select(starts_with(c("Ben", "gender")))%>%
  select(!starts_with(c("Ben_IND")))%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
  select(gender, benscore) %>%
  dplyr::group_by(gender)%>%
  summarise(mean=mean(benscore), sd=sd(benscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= gender, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(y = "mean benefit")
```

## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender.

@@

joineddf$gender <- as.factor(joineddf$gender)
#class(joineddf$gender)
#levels(joineddf$gender)

@@

## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by gender.

@@

joineddf %>%
  select(starts_with(c("Ben", "gender")))%>%
  select(starts_with(c("Ben_IND", "gender")))%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(benscore = mean(c_across(Ben_INDHydro:Ben_INDLPG))) %>%
  select(gender, benscore) %>%
  dplyr::group_by(gender)%>%
  summarise(mean=mean(benscore), sd=sd(benscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= gender, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(y = "mean benefit")
```

## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by religion

@@

joineddf$religion <- as.factor(joineddf$religion)
#class(joineddf$religion)
#levels(joineddf$religion)

joineddf %>%
  select(starts_with(c("Risky", "religion")))%>%
  select(!starts_with(c("Risky_IND", "religiontext")))%>%
 mutate(religion = factor(religion, levels = c("Agnostism/ Atheism","Other (Please mention)" ,  "Jainism", "Buddhism", "Islam",              "Hinduism", "Christanity", "Sikhism"))) %>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
  select(religion, riskscore) %>%
  dplyr::group_by(religion)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= religion, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(y= "mean perceived risk")+
  coord_flip()
```

## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by religion

@@

joineddf %>%
  select(starts_with(c("Ben", "religion")))%>%
  select(!starts_with(c("Ben_IND", "religiontext")))%>%
 mutate(religion = factor(religion, levels = c("Other (Please mention)" ,"Agnostism/ Atheism",  "Christanity","Hinduism", "Islam","Jainism", "Sikhism" ,"Buddhism"))) %>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
  select(religion, benscore) %>%
  dplyr::group_by(religion)%>%
  summarise(mean=mean(benscore), sd=sd(benscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= religion, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(y= "mean perceived benefit")+
  coord_flip()
```

## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by religion.

@@

joineddf$religion <- as.factor(joineddf$religion)
#class(joineddf$religion)
#levels(joineddf$religion)

joineddf %>%
  select(!starts_with(c("religiontext")))%>%
  select(starts_with(c("Risky_IND", "religion")))%>%
 mutate(religion = factor(religion, levels = c("Agnostism/ Atheism", "Jainism","Other (Please mention)" ,  "Buddhism", "Islam",              "Hinduism", "Christanity", "Sikhism"))) %>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
  select(religion, riskscore) %>%
  dplyr::group_by(religion)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= religion, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(y= "mean perceived risk")+
  coord_flip()
```

## Perceived Benefit Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by religion.

@@

joineddf %>%
  select(!starts_with(c("religiontext")))%>%
  select(starts_with(c("Ben_IND", "religion")))%>%
 mutate(religion = factor(religion, levels = c( "Jainism","Other (Please mention)" , "Hinduism","Agnostism/ Atheism", "Islam",   "Christanity","Buddhism", "Sikhism"))) %>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(benscore = mean(c_across(Ben_INDHydro:Ben_INDLPG))) %>%
  select(religion, benscore) %>%
  dplyr::group_by(religion)%>%
  summarise(mean=mean(benscore), sd=sd(benscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= religion, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(y= "mean perceived benefit")+
  coord_flip()
```

## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by age

joineddf$age <- as.factor(joineddf$age)
#class(joineddf$age)
#levels(joineddf$age)

joineddf %>%
  select(starts_with(c("Risky", "age")))%>%
  select(!starts_with(c("Risky_IND")))%>%
 mutate(age = factor(age, levels = c("18-24 years old", "25-34 years old", "35-44 years old", "45-54 years old" , "55-64 years old" ,  "65-74 years old", "75 years or older"))) %>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_Hydro:Risky_Oil))) %>%
  select(age, riskscore) %>%
  dplyr::group_by(age)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= age, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(y = "mean perceived risk")+
  coord_flip()
```

## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by age
```{r, echo=FALSE}

joineddf %>%
  select(starts_with(c("Ben", "age")))%>%
  select(!starts_with(c("Ben_IND")))%>%
 mutate(age = factor(age, levels = c("18-24 years old", "25-34 years old", "35-44 years old", "45-54 years old" , "55-64 years old" ,  "65-74 years old", "75 years or older"))) %>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(benscore = mean(c_across(Ben_Hydro:Ben_Oil))) %>%
  select(age, benscore) %>%
  dplyr::group_by(age)%>%
  summarise(mean=mean(benscore), sd=sd(benscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= age, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(y = "mean perceived benefit")+
  coord_flip()
```

## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by age.

joineddf %>%
  select(starts_with(c("Risky", "age")))%>%
  select(starts_with(c("Risky_IND", "age")))%>%
 mutate(age = factor(age, levels = c("18-24 years old", "25-34 years old", "35-44 years old", "45-54 years old" , "55-64 years old" ,  "65-74 years old", "75 years or older"))) %>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(riskscore = mean(c_across(Risky_INDHydro:Risky_INDLPG))) %>%
  select(age, riskscore) %>%
  dplyr::group_by(age)%>%
  summarise(mean=mean(riskscore), sd=sd(riskscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= age, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "firebrick2")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(y = "mean perceived risk")+
  coord_flip()
```

## Perceived Risk Scores for all individually or community owned energy technologies(small hydro, rooftop solar, windmill, biogas, diesel, kerosene,Firewood/cow dung/crop residue/ coal/charcoal, LPG) by age.

joineddf %>%
  select(starts_with(c("Ben", "age")))%>%
  select(starts_with(c("Ben_IND", "age")))%>%
 mutate(age = factor(age, levels = c("18-24 years old", "25-34 years old", "35-44 years old", "45-54 years old" , "55-64 years old" ,  "65-74 years old", "75 years or older"))) %>%
  #select("Risky_Hydro", "Risky_Solar", "Risky_Nuclear","urban_rural")%>%
  rowwise()%>%
  na.omit()%>%
  dplyr::mutate(benscore = mean(c_across(Ben_INDHydro:Ben_INDLPG))) %>%
  select(age, benscore) %>%
  dplyr::group_by(age)%>%
  summarise(mean=mean(benscore), sd=sd(benscore))%>%
  arrange(desc(mean))%>%
  ggplot(aes(x= age, y = mean))+
  geom_bar(stat="identity", position=position_dodge(), fill = "palegreen3")+
  geom_errorbar(aes(ymin=mean-sd, ymax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  labs(y = "mean perceived benefit")+
  coord_flip()
```

@@

```{r, echo=FALSE}
cenbensummary <- joineddf %>%
  group_by(State)%>%
  summarize_at(vars(starts_with(c("Ben"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Ben_Hydro_mean, Ben_Solar_mean, Ben_Wind_mean, Ben_Nuclear_mean, Ben_Coal_mean, Ben_Gas_mean, Ben_Oil_mean, Ben_Hydro_sd, Ben_Solar_sd, Ben_Wind_sd, Ben_Nuclear_sd, Ben_Coal_sd, Ben_Gas_sd, Ben_Oil_sd) %>%
  select(State, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Ben", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Ben)%>%
  arrange(mean) #%>%
  #setNames(paste0('perceivedrisk.', names(.))) %>%
  #dplyr::rename(technology= perceivedrisk.technology)

## Perceived Risk Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by state

joineddf$State <- as.factor(joineddf$State)
#class(joineddf$State)
#levels(joineddf$State)

cenrisksummary %>%
  mutate(technology = fct_reorder(technology, mean, .desc = TRUE))%>%
  ggplot(aes(y= technology, x= mean, fill = technology))+
  geom_bar(stat="identity", position=position_dodge())+
  theme_minimal()+
  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  scale_fill_manual(values=c("#74238B", "#FEF102","#484349","#BA5C12", "#4D9DE0","#CFEBDF", "#FA6728"))+
  xlim(0,5)+
  facet_wrap(~ State)+
  labs(x = "mean perceived risk", y = "energy technologies")
  #scale_fill_manual(y, values =))+

## Perceived Benefit Scores for all centrally managed energy technologies(nuclear energy, hydroelectric dam, solar energy, wind energy, coal, gas and oil) by state

joineddf$State <- as.factor(joineddf$State)
#class(joineddf$State)
#levels(joineddf$State)

cenbensummary %>%
  mutate(technology = fct_reorder(technology, mean, .desc = TRUE))%>%
  ggplot(aes(y= technology, x= mean, fill = technology))+
  geom_bar(stat="identity", position=position_dodge())+
  theme_minimal()+
  geom_errorbar(aes(xmin=mean-sd, xmax=mean + sd), width=.2,
                 position=position_dodge(.9))+
  scale_fill_manual(values=c("#74238B", "#FEF102","#484349","#BA5C12", "#4D9DE0","#CFEBDF", "#FA6728"))+
  xlim(0,5)+
  facet_wrap(~ State)+
  labs(x = "mean perceived benefit", y = "energy technologies")
  #scale_fill_manual(y, values =))+

```{r, echo=FALSE}
INDrisksummary <- joineddf %>%
  group_by(State)%>%
  summarize_at(vars(starts_with(c("RISKY_IND"))), list(~mean(., na.rm = TRUE), ~median(., na.rm = TRUE), ~sd(.,na.rm = TRUE),~var(.,na.rm = TRUE), ~n())) %>%
  #melt to long format
  gather(key = "technology", value = "summary", Risky_INDHydro_mean, Risky_INDSolar_mean, Risky_INDWind_mean, Risky_INDDiesel_mean, Risky_INDKerosene_mean, Risky_INDFirewoodetc_mean, Risky_INDLPG_mean,  Risky_INDBiogas_mean, Risky_INDHydro_sd, Risky_INDSolar_sd, Risky_INDWind_sd, Risky_INDDiesel_sd, Risky_INDKerosene_sd, Risky_INDBiogas_sd, Risky_INDKerosene_sd, Risky_INDFirewoodetc_sd, Risky_INDLPG_sd) %>%
  select(State, technology, summary) %>%
  # separate risky from variable suffix
  separate(technology, c("Risky", "var"), extra = "merge", fill = "left") %>%
  #separate mean from variable prefix
  separate(var, c("technology", "meansd")) %>%
  # spread summary values back to wide form
  spread(meansd,summary) %>%
  #clean up
  select(-Risky)%>%
  arrange(mean) #%>%
  #setNames(paste0('perceivedrisk.', names(.))) %>%
  #dplyr::rename(technology= perceivedrisk.technology)
